Optimal Algorithms for Dynamic Balanced Graph Partitioning

### 2020-05-14 paper/disc20clustering.tex
Comment

\begin{theorem}	\label{thm:upperbound}
	\PPL reaches the final partition $P_F$
	 and it is $(2\cdot (k-1)\cdot\ell)$-competitive.
\end{theorem}
\begin{proof}
	On each inter-cluster request,
	the algorithm enumerates all component respecting $\ell$-way partitions of components
	that are in the same (closest) distance to $P_I$.
	That is, 
	once it reaches a~partition $P$ at distance $\Delta^* = \Delta(P)$,
	it does not move to a~partition
	$P', \Delta(P') > \Delta^*$,
	before it enumerates all partitions at distance $\Delta^*$.
	Therefore,
	\PPL eventually reaches  the partition $P_F$ at distance $\Delta^*=\OPT$.
	With each distinct request, 
	the size of some component increases by one.
	For any cluster $F_i \in P_F$,
	we have $\sum_{C \in F_i} |C| = k$.
	A component $C \in F_i$,
	 initially begins as an isolated node and it grows by gaining $|C|-1$ more nodes.
	Hence, the total number of times a~component in $F_i$ grows is 
	$\sum_{C \in F_i} (|C|-1) \leq k-1$.
	Therefore, there are at most  $(k-1)\cdot\ell $ distinct requests
	for which \PPL performs a~repartitioning and
	 \PPL performs at most $(k-1)\cdot\ell $ repartitions.
	By Lemma \ref{lemma:rebalancecost},
	each repartitioning costs at most $2\cdot\OPT$.
	The total cost is therefore at most $2\cdot\OPT\cdot (k-1) \cdot\ell$, which implies the competitive ratio.
\end{proof}

>>>>

\begin{theorem}	\label{thm:upperbound}
	\PPL reaches the final partition $P_F$
	 and it is $(2\cdot (k-1)\cdot\ell)$-competitive.
\end{theorem}
\begin{proof}
	\maciek{Maybe: "On each inter-cluster request, the algorithm enumerates all component respecting $\ell$-way partitions in the order of increasing distance to $P_I$" Then we don't need to say i.e.}
	On each inter-cluster request,
	the algorithm enumerates all component respecting $\ell$-way partitions of components
	that are in the same (closest) distance to $P_I$.
	That is, 
	once it reaches a~partition $P$ at distance $\Delta^* = \Delta(P)$,
	it does not move to a~partition
	$P', \Delta(P') > \Delta^*$,
	before it enumerates all partitions at distance $\Delta^*$.
	Therefore,
	\PPL eventually reaches  the partition $P_F$ at distance $\Delta^*=\OPT$.
	With each distinct request, 
	the size of some component increases by one.
	For any cluster $F_i \in P_F$,
	we have $\sum_{C \in F_i} |C| = k$.
	A component $C \in F_i$,
	 initially begins as an isolated node and it grows by gaining $|C|-1$ more nodes.
	Hence, the total number of times a~component in $F_i$ grows is 
	$\sum_{C \in F_i} (|C|-1) \leq k-1$.
	Therefore, there are at most  $(k-1)\cdot\ell $ distinct requests
	for which \PPL performs a~repartitioning and
	 \PPL performs at most $(k-1)\cdot\ell $ repartitions.
	By Lemma \ref{lemma:rebalancecost},
	each repartitioning costs at most $2\cdot\OPT$.
	The total cost is therefore at most $2\cdot\OPT\cdot (k-1) \cdot\ell$, which implies the competitive ratio.
\end{proof}
